### 2011-09-07 docs/architecture/architecture.tex
update directory structure figures
move figure
update GNUmakefile text

\begin{figure}[t]
\centering
\includegraphics[width=5.0in]{\archfigpath/maestro_directory2}
\caption[\maestro\ directory structure]
{The basic \maestro\ directory structure}
\end{figure}

@@

@@

The next two lines define where the top of the source tree is
include the basic Makefile information (like compiler
flags).
\begin{lstlisting}[language={[gnu]make},mathescape=false]
  FPARALLEL := ../..

  include $(FPARALLEL)/mk/GMakedefs.mak
\end{lstlisting}
%$

>>>>

\begin{figure}[t]
\centering
\includegraphics[scale=0.65]{\archfigpath/maestro_directory2}
\caption[\maestro\ directory structure]
{The basic \maestro\ directory structure.}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.65]{\archfigpath/boxlib_directory2}
\caption[\boxlib\ directory structure]
{The basic \boxlib\ directory structure.  The directories used
by \maestro\ are indicated in red.}
\end{figure}

@@

The next line defines where the top of the source tree is located.
\begin{lstlisting}[language={[gnu]make},mathescape=false]
  FPARALLEL := ../..
\end{lstlisting}
